Hierarchical Time Series Forecasting in Emergency Medical Services

### 2022-11-17 manuscript/03-experiment.qmd
Finished work on section 3 for now.

**Naive:** We start with a simple forecasting approach, assuming that the future days will be similar to past days. We use the empirical distribution of the past daily attended incidents to create the forecast distribution of future attended incidents. We consider the empirical distribution of the most recent year of historic data on a rolling basis to capture potential changes in behavior over time.\todo{Actually we use all the data.}

@@

Despite the popularity and the relevance of automatic `ETS` in this study, it may produce forecast distributions that are non-integer and include negative values, despite the number of attended incidents being integer and non-negative. When using `ETS`, a time series transformation approach could be used to generate strictly positive forecasts, although forecast distributions will still be non-integer. An alternative is to use forecasting models that produce integer, non-negative forecasts. In the following section we present Generalized Linear Models (GLMs) and Poisson time series regression to produce count base forecasts.

**Generalized Linear Model (GLM):** GLMs are a family of models developed to extend the concept of linear regression models. They perform a regression by modeling the response variable as coming from a particular member of the exponential family, and then transforming the mean of the response so that the transformed mean is a linear function of the predictors. One of the models that is frequently used in practice to generate count forecasts is the Poisson regression. We will consider forecasting attended incidents using the covariates spline trend, day of the week dummy variables (from Monday to Sunday), Fourier terms to capture yearly seasonality, public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). We fit a Poisson regression model using the function `glm()` from the package in R, with the argument `family = poisson` to specify that we wish to fit a Poisson regression model.

**Poisson Regression using tscount: ** We consider another Poisson regression model that takes into account serial dependence in addition to covariates used in the GLM model. To that end, we use `tsglm()` function in _tscount_ package in R [@JSSv082i05] to model the attended incidents. The logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive. This model can be estimated via maximization of the likelihood function based on Poisson mass function. The regression model captures the short range serial dependence by including the three order autoregressive terms.

**Ensemble method:** we also use an ensemble method that combines forecasts generated from Naive, ETS, GLM and Poisson regression to form a mixture distribution [@combinations].

>>>>

**Naive:** We start with a simple forecasting approach, assuming that the future days will be similar to past days. We use the empirical distribution of the past daily attended incidents to create the forecast distribution of future attended incidents.

@@

Despite the popularity and the relevance of automatic `ETS` in this study, it may produce forecast distributions that are non-integer and include negative values, although the number of attended incidents is always integer and non-negative. When using `ETS`, a time series transformation approach could be used to generate strictly positive forecasts, although forecast distributions will still be non-integer. An alternative is to use forecasting models that produce integer, non-negative forecasts. In the following section we present Generalized Linear Models (GLMs) and Poisson time series regression to produce count base forecasts.

**Generalized Linear Model (GLM):** GLMs are a family of models developed to extend the concept of linear regression models to non-Gaussian distributions [@Faraway2016]. They model the response variable as a particular member of the exponential family, with the mean being a transformation of a linear function of the predictors. One of the models that is frequently used in practice to generate count forecasts is Poisson regression. We will consider forecasting attended incidents using the covariates spline trend, day of the week dummy variables (from Monday to Sunday), Fourier terms to capture yearly seasonality, public holidays (1 when is public holiday, 0 otherwise), school holidays (1 when is school holiday, 0 otherwise) and Christmas Day (1 when is Christmas Day, 0 otherwise) and New Year's Day (1 when is New Year's Day, 0 otherwise). We fit a Poisson regression model using the function `glm()` from the *stats* package in R, with the argument `family = poisson` to specify that we wish to fit a Poisson regression model with a log link function.

**Poisson Regression using tscount:** We also consider another Poisson regression model that takes into account serial dependence, using the `tsglm()` function in the _tscount_ package in R [@JSSv082i05] to model the attended incidents. Again, the logarithmic link function is used to ensure that the parameter of Poisson distribution is always positive. This model captures the short range serial dependence by including three autoregressive terms, in addition to the same covariates that were used in the GLM model. To distinguish this from the previous GLM model, we will refer to this model as "tscount".

**Ensemble method:** Finally, we use an ensemble method that combines the forecasts generated from the Naive, ETS, GLM and tscount models to form a mixture distribution [@combinations].
